Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-06-12 manuscript/manuscript.Rmd
author name change
figure caption adjustment

author: 
  - name          : "Tom E. Hardwicke"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Nieuwe Achtergracht 129B, Department of Psychology, University of Amsterdam, 1018 WT Amsterdam, The Netherlands"
    email         : "tom.hardwicke@uva.nl"
  - name          : "Manuel Bohn"
    affiliation   : "3"
  - name          : "Kyle MacDonald"
    affiliation   : "4"
  - name          : "Emily Hembacher"
    affiliation   : "3"    
  - name          : "Michèle B. Nuijten"
    affiliation   : "5"
  - name          : "Benjamin N. Peloquin"
    affiliation   : "3"
  - name          : "Benny deMayo"
    affiliation   : "3"
  - name          : "Bria Long"
    affiliation   : "3"
  - name          : "Erica J. Yoon"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "3"

@@

```{r scatterPlot, fig.cap="Scatterplot showing reported p-values as a function of reanalysis p-values, classified by reproducibility outcome. Axes are on a log scale. For display purposes, 41 values below 0.001 are not shown.", fig.path="figs/"}
source(here('analysis','plot_reproScatter.R')) # build plot
scatterPlot # show plot
```

>>>>

author: 
  - name          : "Tom E. Hardwicke"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Nieuwe Achtergracht 129B, Department of Psychology, University of Amsterdam, 1018 WT Amsterdam, The Netherlands"
    email         : "tom.hardwicke@uva.nl"
  - name          : "Manuel Bohn"
    affiliation   : "3"
  - name          : "Kyle MacDonald"
    affiliation   : "4"
  - name          : "Emily Hembacher"
    affiliation   : "3"    
  - name          : "Michèle B. Nuijten"
    affiliation   : "5"
  - name          : "Benjamin N. Peloquin"
    affiliation   : "3"
  - name          : "Benjamin E. deMayo"
    affiliation   : "3"
  - name          : "Bria Long"
    affiliation   : "3"
  - name          : "Erica J. Yoon"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "3"

@@

```{r scatterPlot, fig.cap="Scatterplot showing reanalysis p-values as a function of reported p-values, classified by reproducibility outcome. Axes are on a log scale. For display purposes, 41 values below 0.001 are not shown.", fig.path="figs/"}
source(here('analysis','plot_reproScatter.R')) # build plot
scatterPlot # show plot
```
